\documentclass[11pt,a4paper]{article}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage[none]{hyphenat}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\title{Curriculum Vit\ae}
\author{Gordon Reid}
\begin{document}
\section*{Curriculum Vit\ae\ for Gordon Reid}
\section*{Contact information}
Mobile: +44 7706 477 672

Personal Email: gordon.reid1992@hotmail.co.uk

Student Email: 1002536r@student.gla.ac.uk

Skype: gordon-reid

%%% CV HTML GENERATOR START %%%
\section*{Personal Profile}

I am a student with a keen interest in the IT sector. I have an interest in
Machine Learning and Heterogeneous computing, specifically GPGPUs with OpenCL.

My desire is to work in a firm that falls under the aforementioned categories. I
aim to learn and experience everything I can about these career paths, including
the nature of the work, education and training involved, and future job outlook.
With the rapid development of cloud computing, I am particularly interested in
how I can combine these interests as these areas are becoming increasingly
important.

My current projects are available for viewing on my GitHub account:
\url{github.com/gordon1992}

\section*{Education and Qualifications}

\subsection*{September 2010 to present}

I am a matriculated student studying Computing Science at the University of
Glasgow. I have finished the four year of my degree where my results were
equivalent to a first-class honours BSc. From September 2014 I will start my
fifth and final year where I am on track for a first-class honours MSci.

During my fourth year I worked on improving the throughput of a document
filtering system by porting the system to OpenCL to allow the use of GPUs and
other accelerator devices such as the Intel Xeon Phi. The final results were
very encouraging and for my evaluation I was awarded the BCS Prize for Project
with best evaluation.

\subsubsection*{Awards}

June 2014

- Level 4 Honours Class Prize

- BSC Prize - Project with best evaluation (Document Filtering Using OpenCL)

June 2013

- Level 3 Honours Class Prize

June 2012

- Level 2 Class Prize

\subsubsection*{Personal Projects}

Outwith University I am researching my own personal areas of interest, primarily
involving the range of applications that can benefit from GPU acceleration. I
also maintain my own website and VOIP server.

\section*{Work Experience}

\subsection*{June 2014 to August 2014}

\subsubsection*{Software Development Engineer Intern for Amazon}

During the thirteen week internship I worked with a team in Amazon's Edinburgh
Development Centre. I was given the opportunity to work on a wide variety of
tasks including those with high visibility on the Amazon's retail websites.

\subsection*{September 2013 to December 2013}

\subsubsection*{Laboratory Demonstrator}

I was tasked with assisting the third year undergraduates in their Advanced
Programming 3 lab work. Lab work involves C, POSIX threads, and Java
multithreading.

\subsection*{June 2013 to September 2013}

\subsubsection*{Summer IT Analyst for Morgan Stanley}

During the thirteen week internship I was given the responsibility of my own
project. I experienced the full software development life cycle from
requirements gathering and analysis through to quality assurance entry and
eventually to production.

I was the sole developer for an internal web application using Google's Web
Toolkit and Sencha's GXT framework. The application was my first experience of
using these frameworks alongside the Spring framework for the application
configuration. I was able to demonstrate my previous Java abilities and that I
can pick up new and exciting frameworks quickly.

During my time at Morgan Stanley I also had the opportunity to begin learning
the functional programming language Scala which complemented my out of office
learning of Haskell.

\subsection*{August 2011 to January 2013}

\subsubsection*{Back-Of-House Specialist for Apple Retail at Braehead Shopping Centre}

My work included maintaining correctness between physical and systematic
inventory quantities, servicing the shop floor with customer purchases, and
processing deliveries and returns. I worked in a small team with a regular solo
shift where communication was key. This led to me improving my time keeping and
work load management skills.

In addition to this I organised one-day training days for employees working in
other parts of the store to work with us and learn about our day to day
operations. Being able to not only do the job but impart knowledge on other
individuals was a great experience and also improved my knowledge of other parts
of the store.

\section*{Skills}

\subsection*{Languages and Frameworks}

I have working experience in a number of programming and scripting languages,
including C, Java, OpenCL, and Python.

I also have industry experience in using the Spring, GWT, and GXT frameworks.

In addition to those, I also have experience in a number of the latest Web
technologies, including CSS, HTML, Javascript, JQuery, JQueryUI, and PHP.

\subsection*{Miscellaneous}

Practical Grade 5 in Piano

Full clean UK driving licence and car owner since March 2010

%%% CV HTML GENERATOR END %%%

\end{document}
