\documentclass[10pt,a4paper]{article}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage[none]{hyphenat}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\title{Curriculum Vit\ae}
\author{Gordon Reid}
\begin{document}
\section*{Curriculum Vit\ae\ for Gordon Reid}
\section*{Contact information}
Address not present as this version is available online, further information 
available on request.

Mobile: 07706477672

Personal Email: gordon.reid1992@hotmail.co.uk

Student Email: 1002536r@student.gla.ac.uk

Skype: gordon-reid
\section*{Personal Profile}
I am a cheerful and outgoing person who is a good communicator. I am a quick 
learner and have good practical and problem-solving skills along with a 
positive attitude. I am willing to help to the best of my abilities.

I am a student with a keen interest in the IT sector, looking for an 
internship placement to aid my future career prospects and to supplement my 
education.
\section*{Education and Qualifications}
\subsection*{September 2010 to present}
I am a matriculated student studying Computing Science at the University of 
Glasgow, the institution is a member of Universitas 21 and the Russell Group.
I have completed my second year. My exam results average to an A grade and 
for that I was awarded the Level 2 Class Prize for 2011-2012.

The Computing Science course at University is accredited by the British 
Computer Society (BCS) of which I am a student member.

Outwith University I am currently enrolled in several online courses on the 
Coursera website (www.coursera.org). These are fun and challenging courses to 
gain extra knowledge in IT sectors I have an interest in. I also partake in 
courses on Lynda (www.lynda.com) to improve web design knowledge and other 
learn how to use other computer applications such as Blender.
\section*{Work Experience}
\subsection*{August 2011 to Present}
\subsubsection*{Back-Of-House Specialist for Apple Retail at Braehead 
Shopping Centre}
My duties included maintaining correctness between physical and systematic 
inventory quantities, servicing the shop floor with customer purchases and 
processing deliveries and returns. I worked in a small team with a regular 
solo shift where communication was key. This led to me improving my time 
keeping and work load management skills.

In addition to this I organised one-day training days for employees working in 
other parts of the store to work with us and learn about our day to day 
operations. Being able to not only do the job but impart knowledge on other 
individuals was a great experience and also improved my knowledge of other 
parts of the store.
\section*{Skills}
\subsection*{Computer skills}
\subsubsection*{Programming languages}
C, Java, and Python
\subsubsection*{Web development}
CSS, HTML, Javascript, JQuery, PHP, and SQL
\subsubsection*{Operating systems}
All Microsoft Windows distributions since XP

Mac OS X

Debian-based Linux distributions (GUI and CLI). My experience also extends to 
maintaining unmanaged virtual private servers typically used as LAMP servers.
\subsection*{Miscellaneous}
Practical Grade 5 in Piano

Full clean UK driving licence and car owner since March 2010
\section*{References}
Available on request
\end{document}
